Automated Synthesis of State-Space Digital Systems

### 2016-12-28 cav2017/cav2017.tex
combine the 2 CEGIS sections

%-------------------------------
\section{Counter-Example Guided Inductive Synthesis with solution generalisation}
%-------------------------------

This technique relies on parametrising the target language, which
induces a lattice of progressively more expressive languages 
\textcolor{red}{Cristina: Citation?}.  We
start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. As well as giving us an
automatic search procedure, this parametrisation greatly increases the
efficiency of our system since languages low down the lattice are very
easy to decide safety for (i.e. the validation oracle finds an answer
fast). If a program can be synthesised in a low-complexity language,
the whole procedure finishes much faster than if synthesis had been
attempted in a high-complexity language.

\textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
This is text is too generic...}

\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    (verif1) edge node {Generalise} (verif2)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
    ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
   ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
\textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
\end{figure}

  %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Synthesisig the dynamics}\label{sec:cof_synth}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
\begin{enumerate}
\item We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
\begin{enumerate}
\item Calculate $\mat{A}_o,\mat{B}_o,\mat{C}_o$ by rounding down the coefficients $*_{oij}=\mathcal{F}\langle I,F,E\rangle (*_{ij}) : *=\{a,b,c\}$
\item Calculate $\mat{T}$ and $\mat{W}_o^{-1}\mat{W}_{of}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}\eqref{eq:wnof}\eqref{eq:wof}
\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
\item Produce an initial abstraction which corresponds to an unconstrained solution space.
\end{enumerate}
\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F,E \rangle (P,\mat{T})$ be a program describing Jury's method.
\begin{enumerate}
\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F,E\rangle^n$. This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F,E \rangle (P_{a-k},\mat{T})$ that satisfies Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
\item Select the observer error characteristic polynomial $\tilde{\mat{L}} \in \mathbb{R}\langle I,F,E\rangle^n$. 
This is achieved by solving a SAT formula $\mathcal{J}_L=\mathcal{J}\langle I,F,E \rangle (P_p,\mat{W}_o^{-1}\mat{W}_{of})$ 
that satisfies Jury's criteria for 
$P_p=z^n+\sum_{i=1}^n p_i z^{n-i} : p_i \in \vec{P}= (\mat{W}_o^{-1}\mat{W}_{of})^-1 \tilde{\mat{L}} 
+ [\begin{array}{cccc}a_1&a_2&\hdots&a_n\end{array}]^T$.
\item If there is no candidate solution we return UNSAT and exit the loop.
\end{enumerate}
\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
\begin{enumerate}
\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
\end{enumerate} 
\item If the candidate solution is not valid we refine the abstraction used by the synthesiser
\begin{enumerate}
\item Find the constraints that invalidate the property. These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi(\Lambda)$. This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics. 
\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\Lambda}$.
\item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesiser is monotonically decreasing. The first one improves speed of the tool whereas the second ensures convergence.

>>>>

%% %-------------------------------
%% \section{Counter-Example Guided Inductive Synthesis with solution generalisation}
%% %-------------------------------

%% This technique relies on parametrising the target language, which
%% induces a lattice of progressively more expressive languages 
%% \textcolor{red}{Cristina: Citation?}.  We
%% start by attempting to synthesise a program at the lowest point on
%% this lattice and increase the parameters of the language until we
%% reach a point at which the synthesis succeeds. As well as giving us an
%% automatic search procedure, this parametrisation greatly increases the
%% efficiency of our system since languages low down the lattice are very
%% easy to decide safety for (i.e. the validation oracle finds an answer
%% fast). If a program can be synthesised in a low-complexity language,
%% the whole procedure finishes much faster than if synthesis had been
%% attempted in a high-complexity language.

%% \textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
%% This is text is too generic...}

%% \begin{figure}
%% \centering
%% \hspace*{-1cm}
%% \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
%%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
%% },
%%           row sep=1cm, column sep=1.5cm] {
%%    \coordinate (aux1);
%%    \& \coordinate (aux2);
%%    \& ;\\
%%    \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
%%    \&
%%    complexnode/.pic={ 
%%      \node[rectangle,draw,dashed,
%% 	minimum width=6.7cm,
%% 	minimum height=.8cm,
%% 	label={\sc Validation oracles},] (verif) {};
%%    \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
%%    \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
%%    } 
%%    \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
%%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
%%    %% \&
%%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
%%    \& \\
%%    \& \\
%%    \node (gp) {Program Search};
%%    \&
%%    complexnode/.pic={ 
%%      \coordinate (aux);
%%    \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
%%    \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
%%    }   
%%     \\
%%   };

%%    \path
%%     ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
%%     ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
%%     (verif1) edge node {Generalise} (verif2)
%%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
%%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
%%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
%%     ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
%%     (verif2) edge node {} (done)
%%     ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
%%     ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
%%     (aux1) edge (synth.north);
%%    \path[-]
%%    (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
%%    ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);

%% \end{tikzpicture}
%% \caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
%% \textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
%% \end{figure}

%%   %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Synthesisig the dynamics}\label{sec:cof_synth}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{Integrate this paragraph better (Cristina):}
Out CEGIS technique with abstraction refinement
relies on parametrising the target language, which
induces a lattice of progressively more expressive languages.  We
start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. As well as giving us an
automatic search procedure, this parametrisation greatly increases the
efficiency of our system since languages low down the lattice are very
easy to decide safety for (i.e. the validation oracle finds an answer
fast). If a program can be synthesised in a low-complexity language,
the whole procedure finishes much faster than if synthesis had been
attempted in a high-complexity language.

Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
\begin{enumerate}
\item We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
\begin{enumerate}
\item Calculate $\mat{A}_o,\mat{B}_o,\mat{C}_o$ by rounding down the coefficients $*_{oij}=\mathcal{F}\langle I,F,E\rangle (*_{ij}) : *=\{a,b,c\}$
\item Calculate $\mat{T}$ and $\mat{W}_o^{-1}\mat{W}_{of}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}\eqref{eq:wnof}\eqref{eq:wof}
\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
\item Produce an initial abstraction which corresponds to an unconstrained solution space.
\end{enumerate}
\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F,E \rangle (P,\mat{T})$ be a program describing Jury's method.
\begin{enumerate}
\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F,E\rangle^n$. This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F,E \rangle (P_{a-k},\mat{T})$ that satisfies Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
\item Select the observer error characteristic polynomial $\tilde{\mat{L}} \in \mathbb{R}\langle I,F,E\rangle^n$. 
This is achieved by solving a SAT formula $\mathcal{J}_L=\mathcal{J}\langle I,F,E \rangle (P_p,\mat{W}_o^{-1}\mat{W}_{of})$ 
that satisfies Jury's criteria for 
$P_p=z^n+\sum_{i=1}^n p_i z^{n-i} : p_i \in \vec{P}= (\mat{W}_o^{-1}\mat{W}_{of})^-1 \tilde{\mat{L}} 
+ [\begin{array}{cccc}a_1&a_2&\hdots&a_n\end{array}]^T$.
\item If there is no candidate solution we return UNSAT and exit the loop.
\end{enumerate}
\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
\begin{enumerate}
\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
\end{enumerate} 
\item If the candidate solution is not valid we refine the abstraction used by the synthesiser
\begin{enumerate}
\item Find the constraints that invalidate the property. These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi(\Lambda)$. This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics. 
\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\Lambda}$.
\item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesiser is monotonically decreasing. The first one improves speed of the tool whereas the second ensures convergence.
